Chain separation distribution in protein contact networks

### 2020-08-04 paper/main.tex

Protein chain lengths in the PDB vary from small fragments of less than 10 amino acids to large agglomerates of over 2000 residues. The most frequently occurring chain lengths, however are between 100 and 400 residues as shown in Fig.~\ref{fig:pdb_stats}. For the analysis of our theoretical results, we have thus chosen ............ structures of around 200, ........ structures of around 300 and .......... structures of around 400 residues.

 \red{write about how we picked out the specific structures to analyze, (i think we established that 200 to 400 is a very common range of lengths for proteins and i guess we will select them randomly, drawing from "typical" proteins or something), mention how many structures were analyzed and all that stuff.}

>>>>

Protein chain lengths in the PDB vary from small fragments of less than 10 amino acids to large agglomerates of over 2000 residues. The most frequently occurring chain lengths, however are between 100 and 400 residues as shown in Fig.~\ref{fig:pdb_stats}. For the analysis of our theoretical results, we have thus chosen ............ structures of around 200, ........ structures of around 300 and .......... structures of around 400 residues. Those have been converted to PCN's
